SAM simétrico y asimétrico

### 2020-06-29 analysis/paper/paper.Rmd
Removes unnecessary library() call

library(metR)
library(data.table)
library(ggplot2)
library(magrittr)
library(ggh4x)
library(ggperiodic)
library(asymsam)

# source(here("scripts", "helperfun.R"))
# source(here("scripts", "data_locations.R"))
theme_set(theme_asymsam())
ZeroBreaks <- AnchorBreaks(0, NULL, 0)

@@

main_levs <- c(700, 300, 30)
# knitr_set_timer()
# knitr_set_cache(cache.extra = 44)
```

>>>>

library(metR)
library(data.table)
library(ggplot2)
library(magrittr)
library(ggperiodic)
library(asymsam)

theme_set(theme_asymsam())
ZeroBreaks <- AnchorBreaks(0, NULL, 0)

@@

main_levs <- c(700, 300, 30)
```
